Synthesising Termination and Non-Termination Proofs for Bit-Vector Programs

### 2014-10-17 papers/termination/termination-esop/paper.tex
soundness - minor

\section{Soundness, Completeness and Complexity}
%% Termination for bit-vector programs is known to be
%% PSPACE-complete~\cite{DBLP:conf/tacas/CookKRW10}.  We first record the
%% expected results for soundness and completeness of our algorithm for
%% deciding it.  Our strategy for proving soundness and completeness
%% is first to prove that Algorithm~\ref{alg:cegis} (as instantiated
%% with \newC as a background logic) is a semi-decision
%% procedure.
In this section, we show that $\mathcal{L}$ is expressive enough
to compute (non-)termination proofs for every bit-vector program.
By using this result, %We will then combine this result with the fact that the second-order SAT solver is a semi-decision procedure to 
we then show that our technique terminates with a valid proof for every input program.

@@

\begin{theorem}
Our technique %Algorithm~\ref{alg:termination} 
is sound and complete -- it terminates for all input loops $L$ with
 a correct termination verdict.
\end{theorem}

>>>>

\section{Soundness, Completeness and Complexity}
In this section, we show that $\mathcal{L}$ is expressive enough
to compute (non-)termination proofs for every bit-vector program.
By using this result, %We will then combine this result with the fact that the second-order SAT solver is a semi-decision procedure to 
we then show that our analysis terminates with a valid proof for every input program.

@@

\begin{theorem}
Our termination analysis %Algorithm~\ref{alg:termination} 
is sound and complete -- it terminates for all input loops $L$ with
 a correct termination verdict.
\end{theorem}
